---
title: "Cluster-Ethnicity-Passrate"
author: "Lucas Huang (shua440)"
date: "12/09/2019"
output: html_document
---

```{r setup, include=FALSE}
library("dplyr")
library("nortest")
library("car")
library("PMCMRplus")

ca<-read.csv("J:/Lucas/Ethnicity-Cluster/ALLCLUSTER(2014~2019).csv", header=TRUE)

get_cluster <- function(cluster_id){
  return (ca%>%filter(CLUSTER_ID == cluster_id))
}

c1<- get_cluster(1) #1939
c2<- get_cluster(2) #1133
c3<- get_cluster(3) #2298
c4<- get_cluster(4) #2301
c5<- get_cluster(5) #1228
c6<- get_cluster(6) #2876
c7<- get_cluster(7) #2503
c8<- get_cluster(8) #1597
c9<- get_cluster(9) #958
c10<- get_cluster(10) #1727
c11<- get_cluster(11) #1712
c12<- get_cluster(12) #705
c13<- get_cluster(13) #1363
c14<-get_cluster(14) #2311
c15<-get_cluster(15) #2269
c16<- get_cluster(98) #350
c17<-get_cluster(99) #134

#ch <- ca %>% filter(CLUSTER2019 == 3| CLUSTER2019 == 8|CLUSTER2019 == 9|CLUSTER2019 == 10)
#cl <- ca %>% filter(CLUSTER2019 == 1| CLUSTER2019 == 6|CLUSTER2019 == 13)

```




```{r, include=FALSE}
#Assumption Checks Function

library("nortest")
#Normality check for large dataset
norm_check_l <- function (cluster){

  norm1<-lillie.test(cluster$PASSRATE)
  norm2<- boxplot(cluster$PASSRATE~cluster$ETHNICITY,ylab="Pass   Rate",xlab="Ethnicity",col=c("blue","yellow","green"))

  result<- list(norm1,norm2)

  return(result)

}

#Normality check for large dataset
norm_check_s <- function (cluster){

  norm1<-shapiro.test(cluster$PASSRATE)
  norm2<- boxplot(cluster$PASSRATE~cluster$ETHNICITY,ylab="Pass   Rate",xlab="Ethnicity",col=c("blue","yellow","green"))

  result<- list(norm1, norm2)

  return(result)

}


library("car")
#Homogeneity check
homo_check <- function(cluster){
homo1<-leveneTest(cluster$PASSRATE,cluster$ETHNICITY,location=c("mean"))
homo2<-leveneTest(cluster$PASSRATE,cluster$ETHNICITY,location=c("median"))
homo3<-leveneTest(cluster$PASSRATE,cluster$ETHNICITY,location=c("trim.mean"))

result <- list(homo1, homo2, homo3)
return (result)
}





```




## Cluster 1

Normality Check:

```{r, echo=FALSE}

norm_check_l(c1)

```

As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Outliers:

```{r, echo=FALSE}

#outliers
outliersx1<-boxplot(c1$PASSRATE~c1$ETHNICITY, data = c1,
        ylab="Pass Rate",xlab="Ethnicity",
        main = "compare", col = c("#00AFBB", "#E7B800", "#FC4E07")
         )$out

c1<-c1[-which(c1$PASSRATE %in% outliersx1),]

```


Homogeneity check:

```{r, echo=FALSE}
library("car")
homo_check(c1)

```

All p-values are less than 0.05 (level of significance), the results are significant. Homogeneity is not met.
However we still can do ANOVA by accepting assumption that variances not the same and choose Tamhane’s T2.

```{r}
library("PMCMRplus")
fit <- aov(PASSRATE ~ ETHNICITY, data=c1)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c1))
```



## Cluster 2

Normality Check:

```{r, echo=FALSE}

norm_check_l(c2)

```

As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Outliers:

```{r, echo=FALSE}

#outliers
outliersx2<-boxplot(c2$PASSRATE~c2$ETHNICITY, data = c2,
        ylab="Pass Rate",xlab="Ethnicity",
        main = "compare", col = c("#00AFBB", "#E7B800", "#FC4E07")
         )$out

c2<-c2[-which(c2$PASSRATE %in% outliersx2),]

```


Homogeneity check:

```{r, echo=FALSE}
homo_check(c2)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c2)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c2))
```


##Cluster 3

Normality Check:

```{r, echo=FALSE}

norm_check_l(c3)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Outliers:

```{r, echo=FALSE}

outliersx3<-boxplot(c3$PASSRATE~c3$ETHNICITY, data = c3,
        ylab="Pass Rate",xlab="Ethnicity",
        main = "compare", col = c("#00AFBB", "#E7B800", "#FC4E07")
         )$out
print(outliersx3)
c3<-c3[-which(c3$PASSRATE %in% outliersx3),]

```

Homogeneity check:

```{r, echo=FALSE}
homo_check(c3)
```

All p-values are greater than 0.05 (level of significance), the results are not significant. Homogeneity is met.
As a result, we use Tukey multiple pairwise-comparisons.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c3)
summary(fit) 
TukeyHSD(fit) 
```

## Cluster 4

Normality Check:

```{r, echo=FALSE}
norm_check_l(c4)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Outliers:

```{r, echo=FALSE}

outliersx4<-boxplot(c4$PASSRATE~c4$ETHNICITY, data = c4,
        ylab="Pass Rate",xlab="Ethnicity",
        main = "compare", col = c("#00AFBB", "#E7B800", "#FC4E07")
         )$out
print(outliersx4)
c4<-c4[-which(c4$PASSRATE %in% outliersx4),]

```

Homogeneity check:

```{r, echo=FALSE}
homo_check(c4)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c4)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c4)) 

```


## Cluster 5

Normality Check:

```{r, echo=FALSE}
norm_check_l(c5)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Outliers:

```{r, echo=FALSE}

outliersx5<-boxplot(c5$PASSRATE~c5$ETHNICITY, data = c5,
        ylab="Pass Rate",xlab="Ethnicity",
        main = "compare", col = c("#00AFBB", "#E7B800", "#FC4E07")
         )$out
print(outliersx5)
c5<-c5[-which(c5$PASSRATE %in% outliersx5),]

```

Homogeneity check:

```{r, echo=FALSE}
homo_check(c5)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c5)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c5)) 
```



## Cluster 6

Normality Check:

```{r, echo=FALSE}
norm_check_l(c6)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c6)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c6)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c6))
```

## Cluster 7

Normality Check:

```{r, echo=FALSE}
norm_check_l(c7)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c7)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c7)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c7))
```


## Cluster8

Normality Check:

```{r, echo=FALSE}
norm_check_l(c8)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c8)

```

All p-values are greater than 0.05 (level of significance), the results are not significant. Homogeneity is met.
As a result, we use Tukey multiple pairwise-comparisons.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c8)
summary(fit) 
TukeyHSD(fit) 
```


## Cluster 9

Normality Check:

```{r, echo=FALSE}
norm_check_l(c9)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c9)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c9)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c9))

```


Cluster 10

Normality Check:

```{r, echo=FALSE}
norm_check_l(c10)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c10)
```

All p-values are greater than 0.05 (level of significance), the results are not significant. Homogeneity is met.
As a result, we use Tukey multiple pairwise-comparisons.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c10)
summary(fit) 
TukeyHSD(fit) 
```


## Cluster 11

Normality Check:

```{r, echo=FALSE}
norm_check_l(c11)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c11)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c11)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c11))

```



## Cluster 12

Normality Check:

```{r, echo=FALSE}
norm_check_l(c12)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c12)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c12)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c12))

```



## Cluster 13

Normality Check:

```{r, echo=FALSE}
norm_check_l(c13)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c13)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c13)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c13))

```



## Cluster 14

Normality Check:

```{r, echo=FALSE}
norm_check_l(c14)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c14)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c14)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c14))

```



## Cluster 15

Normality Check:

```{r, echo=FALSE}
norm_check_l(c15)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c15)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c15)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c15))

```




## Cluster 16

Normality Check:

```{r, echo=FALSE}
norm_check_s(c16)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c16)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c16)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c16))

```


## Cluster 17

Normality Check:

```{r, echo=FALSE}
norm_check_s(c17)
```
As we can see from the result, p-value< 0.01. The KS tests give  significant results, so the Normality assumption is not satisfied

Homogeneity check:

```{r, echo=FALSE}
homo_check(c17)
```

All p-values are greater than 0.05 (level of significance), the results are significant. Homogeneity is met.
As a result, we use Tamhane’s T2.

```{r}
fit <- aov(PASSRATE ~ ETHNICITY, data=c17)
summary(fit) 
summary(T2 <- tamhaneT2Test(PASSRATE ~ ETHNICITY, data=c17))

```



